---
title: "R Notebook"
output: html_notebook
---


# Read data

```{r}
library(tidyverse)
library(kableExtra)
library(here)

PreToPost.fit.no_boot <- read_rds(here('Fitted model objects','Nonmoderated','Nonbootstrapped','PreToPost.fit'))

PreToPost.fit.boot <- read_rds(here('Fitted model objects','PreToPost.fit.boot'))

```


# Set names of rows and columns

The network model itself does not store the names of the nodes, so input them here manually. Must match the order in which they were entered into the network.

```{r}

var_names <- tibble(names = c('ACTorMEUC','HADS','IESR','FCR','SCS','EAC','AAQc'))
```

# Generic function to create tidy adjacency matrix

```{r}


getTidyAdjacencyMatrix <- function(mgm_fit){
  
  # signs has 0s (undefined values) and NAs (non-sig edge values)
  # in it. We will just replace those with 1s for now.
  signs.tibble <- mgm_fit$pairwise$signs %>% 
    as_tibble() %>%
    mutate(across(everything(), ~replace(.x, .x %in% c(NA,0), 1)))
  
  adjacency.tibble <- mgm_fit$pairwise$wadj %>%
    as_tibble()
  
  # adjacency 
  adjacency_with_signs.tibble <- (signs.tibble * adjacency.tibble)
  
  
  adjacency.long <- 
    adjacency_with_signs.tibble %>%
    
    # rename columns as variable names
    rename_all(~var_names %>% pull(names)) %>%
    
    # add row names as variable names again
    mutate(`Variable 1` = var_names$names) %>%
    
    # format as long by variable 1 and variable 2
    pivot_longer(cols = ACTorMEUC:AAQc, names_to = 'Variable 2') %>%
    mutate(value = round(value,2)) %>%
    
    # remove redundant entries
    
   mutate(Var = map2_chr(`Variable 1`, `Variable 2`, ~toString(sort(c(.x, .y))))) %>%
  distinct(Var, .keep_all = TRUE) %>%
  select(-Var)
  
  return(adjacency.long)
  
}


```

# Function for obtaining estimates and quantiles

Uses part of https://github.com/cran/mgm/blob/master/R/plotRes.R
```{r}


getBootEstimates <- function(object){
  
  # the following is copied from Jonas's code
  
  quantiles <- c(.05, .95)
  
  dims <- dim(object$bootParameters)
    p <- dims[1]
    nB <- dims[3]
    n_pars <- p*(p-1) / 2
    
    # Collapse into edge x property matrix
    tar_mat <- matrix(NA, nrow=n_pars, ncol = 6)
    colnames(tar_mat) <- c("Variable A", "Variable B", "Mean", "qtl_low", "qtl_high", "propLtZ")
    
    counter <- 1
    for(row in 1:p) {
      for(col in row:p) {
        if(row!=col){
          
          # Variable ids
          tar_mat[counter, 1] <- row
          tar_mat[counter, 2] <- col
          
          # Quantiles
          qtls <- quantile(object$bootParameters[row, col, ], probs = quantiles)
          tar_mat[counter, 3] <- mean(object$bootParameters[row, col, ])
          tar_mat[counter, 4] <- qtls[1]
          tar_mat[counter, 5] <- qtls[2]
          tar_mat[counter, 6] <- mean(abs(object$bootParameters[row, col, ]) > 0) # proportion estimates > 0
          
          # update counter
          counter <- counter + 1
        }
      }
    }
    
    # now that the matrix is completed, new code to turn it into a tibble with my variable names embedded
    
    variable_names <- tibble(numbers = as.double(c(1:7)),
                             names = c( 'ACTorMEUC', 'HADS','IESR', 'FCR', 'SCS', 'EAC', 'AAQc'))
    
    EdgeWeights <-
      tar_mat %>%
      as_tibble %>%
      
      # pull in variable names for each variable column
      left_join(variable_names, by = c ("Variable A" = "numbers")) %>%
      select(-`Variable A`) %>%
      rename(`Variable 1` = names) %>%
      left_join(variable_names, by = c ("Variable B" = "numbers")) %>%
      select(-`Variable B`) %>%
      rename(`Variable 2` = names) %>%
      
      # rearrange column order
      relocate(`Variable 2`, .before = Mean) %>%
      relocate(`Variable 1`, .before = `Variable 2`) %>%
      
      # rename columns
      rename(`Mean Boot Estimate of Edge Weight` = Mean,
            `Boot 5%` = qtl_low,
             `Boot 95%` = qtl_high,
             `% Boot Samples Where Edge Was Nonzero` = propLtZ)
    
    return(EdgeWeights)
    
}

```


# Get "type" of association

```{r}
process_vars <- c("AAQc","EAC","SCS")
outcome_vars <- c("IESR","HADS","FCR")

getEdgeType <- function(var_name_1, var_name_2){
  
  case_when(
    
    
    
    # handle intervention effects
    var_name_1 %in% c("ACTorMEUC"), 
     return('Intervention Effect'),
    
    # handle process variable associations
    if_else(var_name_1 %in% process_vars && var_name_2 %in% process_vars,
           return('Process Variable Association'),
           
           # handle outcome variable associations
           if_else(var_name_1 %in% outcome_vars && var_name_2 %in% outcome_vars,
                  return('Outcome Variable Association'),
                  
                  # only remaining option is process-outcome association
                  return('Process-Outcome Association')
           )
    )
  )
  
  
}

```


# Obtain estimates from non-boot model
```{r}

adjacency.no_boot <- getTidyAdjacencyMatrix(PreToPost.fit.no_boot)

```

# Obtain stabilities from boot model

```{r}

estimates.boot <- getBootEstimates(PreToPost.fit.boot)

```

# Combine

```{r}

process_vars <- c("AAQc","EAC","SCS")
outcome_vars <- c("IESR","HADS","FCR")

PreToPost.table <- left_join(adjacency.no_boot, estimates.boot, by = c('Variable 1', 'Variable 2')) %>%
  # drop rows that are association of variable with itself
  filter(!is.na(`Mean Boot Estimate of Edge Weight`)) %>%
  rowwise() %>%
  
  # setup type variable using case_when
  mutate(Type = case_when(
         
         `Variable 1` == "ACTorMEUC" ~ "Intervention Effect",
         `Variable 1` %in% process_vars & `Variable 2` %in% process_vars ~ "Process Variable Associations",
         `Variable 1` %in% outcome_vars & `Variable 2` %in% outcome_vars ~ "Outcome Variable Associations",
         TRUE ~ "Process-Outcome Associations")) %>%
         
         
        
  relocate(Type)


  

PreToPost.table
```