---
title: "Create Table of Combined Sample and Bootstrap Estimates"
author: Joel N Fishbein
output: html_notebook
---

Generates Table 2 and Supplemental Table A1

# Read in libraries

```{r}
library(tidyverse)
library(kableExtra)
library(here)

```

# Read in model fits

## Difference score network model fits

Uncomment this section and comment next section to create table with difference score models

```{r}

# PreToPost.fit.no_boot <- read_rds(here('Fitted model objects','Nonmoderated','Nonbootstrapped','PreToPost.fit'))
# 
# PreToPost.fit.boot <- read_rds(here('Fitted model objects','PreToPost.fit.boot'))
# 
# PreTo6mFU.fit.no_boot <- read_rds(here('Fitted model objects','Nonmoderated','Nonbootstrapped','PreTo6mFU.fit'))
# 
# PreTo6mFU.fit.boot <- read_rds(here('Fitted model objects','PreTo6mFU.fit.boot'))


```

## Residualized change score network model fits

Uncomment this section and comment next section to create table with difference score models
```{r}

PreToPost.fit.no_boot <- read_rds(here('Fitted model objects','Residual Networks','Nonmoderated','Nonbootstrapped','PrePost.residualized.fit'))

PreToPost.fit.boot <- read_rds(here('Fitted model objects','Residual Networks','Nonmoderated','Bootstrapped','PrePost.residualized.boot.fit'))

PreTo6mFU.fit.no_boot <- read_rds(here('Fitted model objects','Residual Networks','Nonmoderated','Nonbootstrapped','PreFU.residualized.fit'))

PreTo6mFU.fit.boot <- read_rds(here('Fitted model objects','Residual Networks','Nonmoderated','Bootstrapped','PreFU.residualized.boot.fit'))




```


# Set names of rows and columns

The network model itself does not store the names of the nodes, so input them here manually. Must match the order in which they were entered into the network.

```{r}

var_names <- tibble(names = c('ACTorMEUC','HADS','IESR','FCR','SCS','EAC','AAQc'))
```

# Generic function to create tidy adjacency matrix

```{r}


getTidyAdjacencyMatrix <- function(mgm_fit){
  
  # signs has 0s (undefined values) and NAs (non-sig edge values)
  # in it. We will just replace those with 1s for now.
  signs.tibble <- mgm_fit$pairwise$signs %>% 
    as_tibble() %>%
    mutate(across(everything(), ~replace(.x, .x %in% c(NA,0), 1)))
  
  adjacency.tibble <- mgm_fit$pairwise$wadj %>%
    as_tibble()
  
  # adjacency 
  adjacency_with_signs.tibble <- (signs.tibble * adjacency.tibble)
  
  
  adjacency.long <- 
    adjacency_with_signs.tibble %>%
    
    # rename columns as variable names
    rename_all(~var_names %>% pull(names)) %>%
    
    # add row names as variable names again
    mutate(`Variable 1` = var_names$names) %>%
    
    # format as long by variable 1 and variable 2
    pivot_longer(cols = ACTorMEUC:AAQc, names_to = 'Variable 2') %>%
    mutate(value = finalfit::round_tidy(value,2)) %>%
    
    # remove redundant entries
    
   mutate(Var = map2_chr(`Variable 1`, `Variable 2`, ~toString(sort(c(.x, .y))))) %>%
  distinct(Var, .keep_all = TRUE) %>%
  select(-Var)
  
  return(adjacency.long)
  
}


```

# Function for obtaining estimates and quantiles

Adapts https://github.com/cran/mgm/blob/master/R/plotRes.R
```{r}


getBootEstimates <- function(object){
  
  # the following is copied from Jonas's code
  
  quantiles <- c(.05, .95)
  
  dims <- dim(object$bootParameters)
    p <- dims[1]
    nB <- dims[3]
    n_pars <- p*(p-1) / 2
    
    # Collapse into edge x property matrix
    tar_mat <- matrix(NA, nrow=n_pars, ncol = 7)
    colnames(tar_mat) <- c("Variable A", "Variable B", "Mean", "qtl_low", "qtl_high", "propGreaterThanZero", "propLessThanZero")
    
    counter <- 1
    for(row in 1:p) {
      for(col in row:p) {
        if(row!=col){
          
          # Variable ids
          tar_mat[counter, 1] <- row
          tar_mat[counter, 2] <- col
          
          # Quantiles
          qtls <- quantile(object$bootParameters[row, col, ], probs = quantiles)
          tar_mat[counter, 3] <- mean(object$bootParameters[row, col, ])
          tar_mat[counter, 4] <- qtls[1]
          tar_mat[counter, 5] <- qtls[2]
          tar_mat[counter, 6] <- mean(object$bootParameters[row, col, ] > 0) # proportion estimates > 0
          tar_mat[counter, 7] <- mean(object$bootParameters[row, col, ] < 0) # proportion estimates < 0
          
          # update counter
          counter <- counter + 1
        }
      }
    }
    
    # now that the matrix is completed, new code to turn it into a tibble with my variable names embedded
    
    variable_names <- tibble(numbers = as.double(c(1:7)),
                             names = c( 'ACTorMEUC', 'HADS','IESR', 'FCR', 'SCS', 'EAC', 'AAQc'))
    
    EdgeWeights <-
      tar_mat %>%
      as_tibble %>%
      
      # pull in variable names for each variable column
      left_join(variable_names, by = c ("Variable A" = "numbers")) %>%
      select(-`Variable A`) %>%
      rename(`Variable 1` = names) %>%
      left_join(variable_names, by = c ("Variable B" = "numbers")) %>%
      select(-`Variable B`) %>%
      rename(`Variable 2` = names) %>%
      
      # rearrange column order
      relocate(`Variable 2`, .before = Mean) %>%
      relocate(`Variable 1`, .before = `Variable 2`) %>%
      
      # rename columns
      rename(`Mean Boot Estimate of Edge Weight` = Mean,
            `Boot 5%` = qtl_low,
             `Boot 95%` = qtl_high,
             `Greater Than Zero %` = propGreaterThanZero, 
            `Less Than Zero %` = propLessThanZero) %>%
      
      
      # for stability, we want to see % boot samples with edge being nonzero and in same direction as boot estimate
      # boot estimate and sample estimate have same direction in all cases (or sample estimate is 0)
      # thus, use direction of boot estimate here to dictate which % is stored for display as Stability %
      mutate(`Bootstrap Stability %` = ifelse(`Mean Boot Estimate of Edge Weight` > 0,
                                              `Greater Than Zero %`, 
                                              `Less Than Zero %`))
    
    return(EdgeWeights)
    
}

```


# Get "type" of association

```{r}
process_vars <- c("AAQc","EAC","SCS")
outcome_vars <- c("IESR","HADS","FCR")

getEdgeType <- function(var_name_1, var_name_2){
  
  case_when(
    
    
    
    # handle intervention effects
    var_name_1 %in% c("ACTorMEUC"), 
     return('Intervention Effect'),
    
    # handle process variable associations
    if_else(var_name_1 %in% process_vars && var_name_2 %in% process_vars,
           return('Process Variable Association'),
           
           # handle outcome variable associations
           if_else(var_name_1 %in% outcome_vars && var_name_2 %in% outcome_vars,
                  return('Outcome Variable Association'),
                  
                  # only remaining option is process-outcome association
                  return('Process-Outcome Association')
           )
    )
  )
  
  
}

```


# Combine non boot and boot models

```{r}

getCombinedNonBootandBootEstimates <- function(model.no_boot.fit, model.boot.fit) {
  
  adjacency.no_boot <- getTidyAdjacencyMatrix(model.no_boot.fit)
  
  boot.estimates <- getBootEstimates(model.boot.fit)
  
  
  process_vars <- c("AAQc","EAC","SCS")
  outcome_vars <- c("IESR","HADS","FCR")
  
  combined.table <- left_join(adjacency.no_boot, boot.estimates, by = c('Variable 1', 'Variable 2')) %>%
    # drop rows that are association of variable with itself
    filter(!is.na(`Mean Boot Estimate of Edge Weight`)) %>%
    
    rename(`Sample Estimate` = value) %>%
    
    # setup type variable using case_when
    mutate(Type = case_when(
      
      `Variable 1` == "ACTorMEUC" ~ "Intervention Effects",
      `Variable 1` %in% process_vars & `Variable 2` %in% process_vars ~ "Process Variable Associations",
      `Variable 1` %in% outcome_vars & `Variable 2` %in% outcome_vars ~ "Outcome Variable Associations",
      TRUE ~ "Process-Outcome Associations")) %>%
    
    mutate(Type = factor(Type,
                         levels = c("Intervention Effects",
                                    "Process Variable Associations",
                                    "Outcome Variable Associations",
                                    "Process-Outcome Associations"))) %>%
    
    
    
    
    relocate(Type) %>%
    
    arrange(Type) %>%
    
    mutate(across(is.numeric, ~round(.x,2))) %>%
    
    mutate(`Boostrap Mean [95% Quantile] Estimate` = str_c(`Mean Boot Estimate of Edge Weight`, 
                                                     ' [',
                                                     `Boot 5%`,
                                                     ', ',
                                                     `Boot 95%`,
                                                     ']')) %>%
    
    relocate(`Boostrap Mean [95% Quantile] Estimate`, .after = `Sample Estimate`) %>%
    
    # make this into a percentage
    mutate(`Inclusion %` = `Bootstrap Stability %`* 100) %>%
    
    select(-`Mean Boot Estimate of Edge Weight`,-`Boot 5%`,-`Boot 95%`, -`Bootstrap Stability %`,
            -`Greater Than Zero %`, -`Less Than Zero %`)
  
}


```

# Obtain estimates from non-boot model
```{r}

PreToPost.adjacency.no_boot <- getTidyAdjacencyMatrix(PreToPost.fit.no_boot)

PreTo6mFU.adjacency.no_boot <- getTidyAdjacencyMatrix(PreTo6mFU.fit.no_boot)

```

# Obtain stabilities from boot model

```{r}

PreToPost.estimates.boot <- getBootEstimates(PreToPost.fit.boot)

PreTo6mFU.estimates.boot <- getBootEstimates(PreTo6mFU.fit.boot)

```

# Combine

```{r}

PreToPost.table <- getCombinedNonBootandBootEstimates(PreToPost.fit.no_boot, PreToPost.fit.boot)
PreTo6mFU.table <- getCombinedNonBootandBootEstimates(PreTo6mFU.fit.no_boot, PreTo6mFU.fit.boot)

```

# Print

```{r}

PreToPost.table

```

```{r}

PreTo6mFU.table

```
