---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---



```{r}
library(tidyverse)
library(kableExtra)
library(tableone)
library(here)

```

# Identify participants with complete data at Pre and Post for our variables in the network

```{r}

complete_data <- read_rds(file = here('4 Generated Datasets','Vars_At_All_Timepoints.rds')) %>%
  select(-CESD) %>%
  pivot_longer(cols = HADS.A:AAQc) %>%
  filter(timepoint %in% c("1","3")) %>%
  pivot_wider(names_from = timepoint:name) %>%
  filter(complete.cases(across(everything())))

network_analysis_IDs <- complete_data %>% pull(ID)
```


# Read in Valued Living demographics data

```{r}

demographicsDB <- read_rds(here('4 Generated Datasets','outcomesDB_for_TableOne.rds')) %>% 
  filter(ID %in% network_analysis_IDs) %>%
  mutate(IncomeAtLeast61K = ifelse(Income %in% c('$61,000 - $80,000',
                                                 "$81,000 - $100,000", 
                                                                "$101,000 - $150,000",
                                                                "$151,000 +"), TRUE, FALSE))
                                                 



```


## Find median income
```{r}

demographicsDB %>%
  select(Income) %>%
  arrange(Income) %>%
  slice(round(113/2,0))

demographicsDB %>%
  select(Income) %>%
  unique()

```

## Find median education
```{r}

demographicsDB %>%
  select(Education) %>%
  arrange(Education) %>%
  slice(round(113/2,0))

demographicsDB %>%
  select(Income) %>%
  unique()

```

```{r}



```

# Collapse down Income and Education to make larger cell sizes to preserve anonymity

```{r}

demographicsDB <- demographicsDB %>%
  mutate(IncomeCollapsed = forcats::fct_collapse(.f = Income, 
                                                 `$0-20,000` = c("0 - $10,000",
                                                                "$11,000 - $20,000")
                                                                "$21,000 - $30,000",
                                                                "$31,000 - $40,000"),
                                                 `$21-80,000` = c(  "$21,000 - $30,000",
                                                                "$31,000 - $40,000",
                                                                "$41,000 - $60,000", 
                                                                  "$61,000 - $80,000"),
                                                 `$81,000+` = c("$81,000 - $100,000", 
                                                                "$101,000 - $150,000",
                                                                "$151,000 +")),
         EducationCollapsed = forcats::fct_collapse(.f = Education,
                                                    `Less than Associate Degree` = 
                                                      c("Some high school",
                                                        "High school diploma / GED",
                                                        "Some college"),
                                                    `Associates or Bachelors Degree` =
                                                      c("2 year college degree",
                                                        "Bachelor's degree"),
                                                    `Graduate or Professional Degree` = 
                                                      c("Graduate degree (MA, PhD)",
                                                        c("Professional degree (MD, JD, MBA)") )))
  

```




# Pre-Post Table

Save the following to a .txt file, then open in Excel

```{r}

covidACTvsMEUCTable <- CreateTableOne(data = demographicsDB,
               strata = 'Condition',
               vars = c('Age', 
                        'isFemale',
                        'isWhite',
                        "IncomeAtLeast61K",
                        'atLeastAssociatesDegree',
                        'isStage0toII',
                        'hasBreastCancer',
                        'HAD_T1',
                        'CARS_T1',
                        'IESR.Total_T1',
                        'AAQc_T1',
                        'SelfComp_Mean_T1',
                        'EAC_Mean_T1'
                        ))
               

print(covidACTvsMEUCTable,
      catDigits = 2,
      nospaces = TRUE,
      explain = TRUE,
      format = 'pf',
      quote = TRUE)
      # denote which variables should be compared with Fisher's
      # exact test due to small cell size
#          
```


# Do separate table for Pre-FU for supplemental table

# Identify participants with complete data at Pre and FU for our variables in the network

```{r}

complete_data_Pre_FU <- read_rds(file = here('4 Generated Datasets','Vars_At_All_Timepoints.rds')) %>%
  select(-CESD) %>%
  pivot_longer(cols = HADS.A:AAQc) %>%
  filter(timepoint %in% c("1","5")) %>%
  pivot_wider(names_from = timepoint:name) %>%
  filter(complete.cases(across(everything())))

network_analysis_IDs <- complete_data_Pre_FU %>% pull(ID)
```


# Read in Valued Living demographics data

```{r}

demographicsDB <- read_rds(here('4 Generated Datasets','outcomesDB_for_TableOne.rds')) %>% 
  filter(ID %in% network_analysis_IDs) %>%
  mutate(IncomeAtLeast61K = ifelse(Income %in% c('$61,000 - $80,000',
                                                 "$81,000 - $100,000", 
                                                                "$101,000 - $150,000",
                                                                "$151,000 +"), TRUE, FALSE))
                                                 



```


# Collapse down Income and Education to make larger cell sizes to preserve anonymity

```{r}

demographicsDB <- demographicsDB %>%
  mutate(IncomeCollapsed = forcats::fct_collapse(.f = Income, 
                                                 `$0-20,000` = c("0 - $10,000",
                                                                "$11,000 - $20,000",
                                                                "$21,000 - $30,000",
                                                                "$31,000 - $40,000"),
                                                 `$21-80,000` = c(  "$21,000 - $30,000",
                                                                "$31,000 - $40,000",
                                                                "$41,000 - $60,000", 
                                                                  "$61,000 - $80,000"),
                                                 `$81,000+` = c("$81,000 - $100,000", 
                                                                "$101,000 - $150,000",
                                                                "$151,000 +")),
         EducationCollapsed = forcats::fct_collapse(.f = Education,
                                                    `Less than Associate Degree` = 
                                                      c("Some high school",
                                                        "High school diploma / GED",
                                                        "Some college"),
                                                    `Associates or Bachelors Degree` =
                                                      c("2 year college degree",
                                                        "Bachelor's degree"),
                                                    `Graduate or Professional Degree` = 
                                                      c("Graduate degree (MA, PhD)",
                                                        c("Professional degree (MD, JD, MBA)") )))
  

```




# Compare Covid Sample ACT and UC

Save the following to a .txt file, then open in Excel

```{r}

covidACTvsMEUCTable <- CreateTableOne(data = demographicsDB,
               strata = 'Condition',
               vars = c('Age', 
                        'isFemale',
                        'isWhite',
                        "IncomeAtLeast61K",
                        'atLeastAssociatesDegree',
                        'isStage0toII',
                        'hasBreastCancer',
                        'GAD7_T1',
                        'CARS_T1',
                        'IESR.Total_T1',
                        'AAQc_T1',
                        'SelfComp_Mean_T1',
                        'EAC_Mean_T1'
                        ))
               

print(covidACTvsMEUCTable,
      catDigits = 2,
      nospaces = TRUE,
      explain = TRUE,
      format = 'pf',
      quote = TRUE)
      # denote which variables should be compared with Fisher's
      # exact test due to small cell size
#          
```


