---
title: "Difference Score Mediation Models"
output: html_notebook
---

# read data and libraries

```{r}

library(tidyverse)
library(here)
library(lavaan)


# PreToPost.data <- readRDS(file = here('4 Generated Datasets','Vars_At_All_Timepoints.rds')) %>%
#   as_tibble() %>%
#   select(-CESD) %>%
#   pivot_longer(cols = HADS.A:AAQc) %>%
#   filter(timepoint %in% c(1,3)) %>%
#   pivot_wider(names_from = timepoint:name, names_glue = "{name}_T{timepoint}") %>%
#   filter(complete.cases(.))
```

# Run models with simple lavaan code (using precalculated residual scores)

## Read in residualized scores (computed in the script that runs the residualized change score network models)

```{r}

PrePost.residualized.tibble <- read_rds(file = here('4 Generated Datasets',
                                          'residualized.PrePost.tibble'))

PreFU.residualized.tibble <- read_rds(file = here('4 Generated Datasets',
                                          'residualized.PreFU.tibble'))

```

## Generic mediation model

### Pre-Post

```{r}

runPrePostMediationModel <- function(mediator_var, outcome_var) {
  mediation.model.generic <- '

Mediator.PrePost.resid ~ a*Condition_Dummy
Outcome.PrePost.resid ~ b*Mediator.PrePost.resid
Outcome.PrePost.resid ~ cprime*Condition_Dummy

# !Estimate of mediated effect;
ab := a*b

'
  # this line inserts the actual variable names into the model syntax
  # as specified above
  mediation.model <-  str_replace_all(mediation.model.generic,
                                      c("Outcome" = outcome_var,
                                        "Mediator" = mediator_var))
  # model is estimated
  mediation.fit <- lavaan::sem(model = mediation.model,
                               data = PrePost.residualized.tibble,
                               bootstrap = 10000,
                               se = 'bootstrap',
                               missing = 'fiml')
  return(mediation.fit)
}

```

### Pre-FU

```{r}

runPreFUMediationModel <- function(mediator_var, outcome_var) {
  mediation.model.generic <- '

Mediator.PreFU.resid ~ a*Condition_Dummy
Outcome.PreFU.resid ~ b*Mediator.PreFU.resid
Outcome.PreFU.resid ~ cprime*Condition_Dummy


# !Estimate of mediated effect;
ab := a*b

'
  # this line inserts the actual variable names into the model syntax
  # as specified above
  mediation.model <-  str_replace_all(mediation.model.generic,
                                      c("Outcome" = outcome_var,
                                        "Mediator" = mediator_var))
  # model is estimated
  mediation.fit <- lavaan::sem(model = mediation.model,
                               data = PreFU.residualized.tibble,
                               bootstrap = 10000,
                               se = 'bootstrap',
                               missing = 'fiml')
  return(mediation.fit)
}

```

## Run models

## EAC Models

```{r}
set.seed(1)
EAC.Mean_IESR.Total_contemporaneous.fit <- runPrePostMediationModel('EAC.Total','IESR.Total')

set.seed(1)
EAC.Mean_FCR_contemporaneous.fit <- runPrePostMediationModel('EAC.Total','FCR')


set.seed(1)
EAC.Mean_HADS.A_contemporaneous.fit <- runPrePostMediationModel('EAC.Total','HADS.A')

```

## SCS Models

```{r}
set.seed(1)
SCS_IESR.Total_contemporaneous.fit <- runPrePostMediationModel('SCS','IESR.Total')
set.seed(1)
SCS_FCR_contemporaneous.fit <- runPrePostMediationModel('SCS','FCR')
set.seed(1)
SCS_HADS.A_contemporaneous.fit <- runPrePostMediationModel('SCS','HADS.A')
```

## AAQc Models

```{r}
set.seed(1)
AAQc_IESR.Total_contemporaneous.fit <- runPrePostMediationModel('AAQc','IESR.Total')
set.seed(1)
AAQc_FCR_contemporaneous.fit <- runPrePostMediationModel('AAQc','FCR')
set.seed(1)
AAQc_HADS.A_contemporaneous.fit <- runPrePostMediationModel('AAQc','HADS.A')
```

# save model output to a file

Since these models take a long time to run, save the actual output.

```{r}
# remove objects from the environment
# so that individual scores are not saved alongside the models
rm(PrePost.residualized.tibble)
rm(PreFU.residualized.tibble)
rm(runPreFUMediationModel)
rm(runPrePostMediationModel)
# save the rest of the workspace, which is now just lavaan fit models
# and the generic functions
save.image(file = here('4 Generated Datasets', 'PrePost_mediation_models_residualized.RData'))
```

# CODE NOT IN USE BELOW

# Valente and Mackinnon way

Lavaan syntax adapted from Mplus syntax provided in Valente and MacKinnon 2017.

Those authors describe a two-step process for estimating these models:

1.  Run a simple regression of posttest scores on pretest scores for use in the residualized change score models
2.  Run the residualized change score models using values from the simple regressions in step 1

The Mplus code they provide for Step 1 is as follows:				

``` Mplus
deltam BY m2@1;
deltam@0;
[deltam];
m2 on m1;
m2;
[m2@0 m1];

deltay BY y2@1;
deltay@0;
[deltay];
y2 on y1;
y2;
[y2@0 y1];

m2 with y2@0;
m1 with y1; 
m1 with deltam@0;
m1 with deltay @0;
y1 with deltam@0;
y1 with deltay @0;
deltay with deltam@0;
```

My analogous lavaan code is as follows:

```{r}

simple.regression.model <-
'
# latent mediator change variable
mediator_change =~   1*MediatorVariable_T3
mediator_change ~~ 0*mediator_change
mediator_change ~ mediator_change_mean*1


MediatorVariable_T3 ~ MediatorVariable_T1
MediatorVariable_T3 ~~ MediatorVariable_T3

MediatorVariable_T3 ~ 0
MediatorVariable_T1 ~ 1

# latent outcome change variable
outcome_change =~   1*outcomeVariable_T3
outcome_change ~~ 0*outcome_change
outcome_change ~ outcome_change_mean*1


outcomeVariable_T3 ~ outcomeVariable_T1
outcomeVariable_T3 ~~ outcomeVariable_T3

outcomeVariable_T3 ~ 0
outcomeVariable_T1 ~ 1


# mediator - outcome associations
m2 with y2@0;
m1 with y1; 
m1 with deltam@0;
m1 with deltay @0;
y1 with deltam@0;
y1 with deltay @0;
deltay with deltam@0;


MediatorVariable_T3 ~~ 0*outcomeVariable_T3
MediatorVariable_T1 ~~ outcomeVariable_T1

MediatorVariable_T1 ~~ 0*mediator_change
MediatorVariable_T1 ~~ 0*outcome_change
outcomeVariable_T1 ~~ 0*mediator_change
outcomeVariable_T1 ~~ 0*outcome_change

outcome_change ~~ 0*mediator_change

'

```

					
				
			
		

	

					
				
			
		

	

The Mplus syntax they provide for Step 2 is as follows:

``` Mplus
deltam BY m2@1;
deltam;
[deltam];

!@0.189 is the estimate of the simple regression of M2 on M1;
m2 on m1@0.189;
m2 with m1@0;
m2@0;			
[m2@0 m1];
deltay BY y2@1;
deltay;
[deltay];

!@0.418 is the estimate of the simple regression of Y2 on Y1;
y2 on y1@0.418;
y2 with y1@0;
y2@0;
[y2@0 y1];

!Regressing Mchange on X. Equivalent to Res change;
deltam on x (a);

!Regressing Ychange on Mchange and X. Equivalent to Res change;
deltay on x
deltam (b);
m1 with y1;

Model constraint:
NEW(med);
med=a*b; !Estimate of mediated effect;
```

Here is my R code:

```{r}

runMediationModel <- function(mediator_var, outcome_var) {
  mediation.model.generic <- '

# latent mediator change variable
mediator_change =~   1*MediatorVariable_T3
mediator_change ~ mediator_change_mean*1
mediator_change ~~ mediator_variance*mediator_change


MediatorVariable_T3 ~ 1*MediatorVariable_T1
MediatorVariable_T3 ~~ 0*MediatorVariable_T1
MediatorVariable_T3 ~~ 0*MediatorVariable_T3
MediatorVariable_T3 ~ 0
MediatorVariable_T1 ~ 1

# latent outcome change variable
outcome_change =~   1*OutcomeVariable_T3
outcome_change ~ outcome_change_mean*1
outcome_change ~~ outcome_variance*outcome_change

#Constraining the stability of the outcome to 0
OutcomeVariable_T3 ~ 1*OutcomeVariable_T1
OutcomeVariable_T3 ~~ 0*OutcomeVariable_T1
OutcomeVariable_T3 ~~ 0*OutcomeVariable_T3
OutcomeVariable_T3 ~ 0
OutcomeVariable_T1 ~ 1

# Estimating the pretest correlation between M1 and Y1 and variance of X
OutcomeVariable_T1 ~~ covariance_at_T1*MediatorVariable_T1


# a path
mediator_change ~ a*Condition_Dummy

# mediator stability
mediator_change ~ mediator_stability*MediatorVariable_T1

# change in mediator regressed on baseline outcome
mediator_change ~ mediator_change_x_outcome_T1*OutcomeVariable_T1


# cprime path
outcome_change ~ cprime*Condition_Dummy

# b path
outcome_change ~ b*mediator_change

# change in outcome regressed on baseline mediator
outcome_change ~  outcome_change_x_mediator_T1*MediatorVariable_T1

# stability of outcome 
outcome_change ~ outcome_stability*OutcomeVariable_T1

# !Estimate of mediated effect;
ab := a*b

effect_size := ab/sqrt(outcome_variance)
'
  # this line inserts the actual variable names into the model syntax
  # as specified above
  mediation.model <-  str_replace_all(mediation.model.generic,
                                      c("OutcomeVariable" = outcome_var,
                                        "MediatorVariable" = mediator_var))
  # model is estimated
  mediation.fit <- lavaan::sem(model = mediation.model,
                               data = PreToPost.data,
                               bootstrap = 10000,
                               se = 'bootstrap',
                               missing = 'fiml')
  return(mediation.fit)
}


```

## EAC Models

```{r}
set.seed(1)
EAC.Mean_IESR.Total_contemporaneous.fit <- runMediationModel('EAC.Total','IESR.Total')

set.seed(1)
EAC.Mean_FCR_contemporaneous.fit <- runMediationModel('EAC.Total','FCR')


set.seed(1)
EAC.Mean_HADS.A_contemporaneous.fit <- runMediationModel('EAC.Total','HADS.A')

```

## SCS Models

```{r}
set.seed(1)
SCS_IESR.Total_contemporaneous.fit <- runMediationModel('SCS','IESR.Total')
set.seed(1)
SCS_FCR_contemporaneous.fit <- runMediationModel('SCS','FCR')
set.seed(1)
SCS_HADS.A_contemporaneous.fit <- runMediationModel('SCS','HADS.A')
```

## AAQc Models

```{r}
set.seed(1)
AAQc_IESR.Total_contemporaneous.fit <- runMediationModel('AAQc','IESR.Total')
set.seed(1)
AAQc_FCR_contemporaneous.fit <- runMediationModel('AAQc','FCR')
set.seed(1)
AAQc_HADS.A_contemporaneous.fit <- runMediationModel('AAQc','HADS.A')
```

# 
