---
author: Joel N. Fishbein, M.A.
date: December 11, 2022
---

# Read in the data and libraries

```{r}

library(tidyverse)
library(here)
library(lavaan)
library(semTools)

``` 

# Identify participants with complete data at Pre and Post for our variables in the network

```{r}

complete_data <- read_rds(file = here('4 Generated Datasets','Vars_At_All_Timepoints.rds')) %>%
  select(-CESD) %>%
  pivot_longer(cols = HADS.A:AAQc) %>%
  filter(timepoint %in% c("1","3")) %>%
  pivot_wider(names_from = timepoint:name) %>%
  filter(complete.cases(across(everything())))
  
  
network_analysis_IDs <- complete_data %>% pull(ID)


```

# Read in item level data 

```{r}

itemsDB <- read_csv('~/On HD/Raw data/Valued Living Study/RCT_Qualtrics_Unabridged_6.8.21.csv', na = "#NULL!") %>%
  filter(ID %in% network_analysis_IDs)

```


# Compute omega total

The procedure here of calling lavaan first with the defaults as used here, and them semTools to obtain reliability estimates, is described in https://doi-org.colorado.idm.oclc.org/10.1177%2F2515245920951747

## CARS

omega  0.8514432

```{r}

CARS.model <-
  'factor =~ Recur_Q1_T1 + 
  Recur_Q2_T1 + 
  Recur_Q3_T1 + 
  Recur_Q4_T1'

CARS.fit <- lavaan::cfa(CARS.model, 
                        data=itemsDB, 
                        std.lv=T, 
                        missing='direct', 
                        estimator='MLR')


semTools::reliability(CARS.fit)
  

```


## EAC

omega  0.9126759

HEADS UP: Question 1 on EAC is the instructions, so you have to include Question 9.

```{r}

EAC.model <-
  'factor =~ EAC_Q9_T1 + EAC_Q2_T1 +
         EAC_Q3_T1 + EAC_Q4_T1 +
         EAC_Q5_T1 + EAC_Q6_T1 +
         EAC_Q7_T1 + EAC_Q8_T1'

EAC.fit <- lavaan::cfa(EAC.model, 
                        data=itemsDB, 
                        std.lv=T, 
                        missing='direct', 
                        estimator='MLR')

semTools::reliability(EAC.fit)

```


## AAQc
omega  0.8327712

```{r}

AAQc.model <-
  'factor =~ AAQ_Q1_T1 +
  AAQ_Q2_T1 +
  AAQ_Q3_T1 +
  AAQ_Q4_T1 +
  AAQ_Q5_T1 +
  AAQ_Q6_T1 +
  AAQ_Q7_T1 +
  AAQ_Q8_T1 +
  AAQ_Q9_T1 +
  AAQ_Q10_T1 +
  AAQ_Q11_T1 +
  AAQ_Q12_T1 +
  AAQ_Q13_T1 +
  AAQ_Q14_T1 +
  AAQ_Q15_T1'


AAQc.fit <- lavaan::cfa(AAQc.model, 
                        data=itemsDB, 
                        std.lv=T, 
                        missing='direct', 
                        estimator='MLR')

semTools::reliability(AAQc.fit)
```


## HADS-A

HEADS UP: Question 1 on EAC is the instructions, so you have to include Question 8.

omega  0.8215879
```{r}

HADSA.model <-
  'factor =~ HADS_Q2_T1 +
  HADS_Q3_T1 +
  HADS_Q4_T1 +
  HADS_Q5_T1 +
  HADS_Q6_T1 +
  HADS_Q7_T1 +
  HADS_Q8_T1'



HADSA.fit <- lavaan::cfa(HADSA.model, 
                        data=itemsDB, 
                        std.lv=T, 
                        missing='direct', 
                        estimator='MLR')

semTools::reliability(HADSA.fit)
```





## Self Compassion

omega  0.8711170

```{r}

SelfCompassion.model <-
  'factor =~ SCSSF_Q1_T1R +
  SCSSF_Q2_T1 +
  SCSSF_Q3_T1 +
  SCSSF_Q4_T1R +
  SCSSF_Q5_T1 +
  SCSSF_Q6_T1 +
  SCSSF_Q7_T1 +
  SCSSF_Q8_T1R +
  SCSSF_Q9_T1R +
  SCSSF_Q10_T1 +
  SCSSF_Q11_T1R +
  SCSSF_Q12_T1R'




SelfCompassion.fit <- lavaan::cfa(SelfCompassion.model, 
                        data=itemsDB, 
                        std.lv=T, 
                        missing='direct', 
                        estimator='MLR')

semTools::reliability(SelfCompassion.fit)
```




## IES Total

omega  0.8534838

```{r}

IESR.model <-
  'factor =~ IES_Q1_T1 +
  IES_Q2_T1 +
  IES_Q3_T1 +
  IES_Q4_T1 +
  IES_Q5_T1 +
  IES_Q6_T1 +
  IES_Q7_T1 +
  IES_Q8_T1 +
  IES_Q9_T1 +
  IES_Q10_T1 +
  IES_Q11_T1 +
  IES_Q12_T1 +
  IES_Q13_T1 +
  IES_Q14_T1 +
  IES_Q15_T1 +
  IES_Q16_T1 +
  IES_Q17_T1 +
  IES_Q18_T1 +
  IES_Q19_T1 +
  IES_Q20_T1 +
  IES_Q21_T1 +
  IES_Q22_T1'




IESR.fit <- lavaan::cfa(IESR.model, 
                        data=itemsDB, 
                        std.lv=T, 
                        missing='direct', 
                        estimator='MLR')

semTools::reliability(IESR.fit)
```

