---
title: "Estimate network models"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---


# Read in the data and libraries

```{r}

knitr::opts_chunk$set(error = TRUE)

library(tidyverse)
library(mgm)
library(qgraph)
library(psych)
library(corrr)
library(here)

``` 

```{r}

data_all_timepoints <- read_rds(file = here('4 Generated Datasets','Vars_At_All_Timepoints.rds'))

```

# Generic model functions


## fit MGM functions
```{r}

fit_my_mgm <- function(my_data){
  
  set.seed(08132021)
  fit_mgm <- mgm::mgm(data = my_data, 
                      
                      # first variable (condition) has 2 conditions, all others are continuous
                      level = c(2,1,1,1,1,1,1), 
                      
                      # first variable (condition) is categorical, all others 
                      # have assumed Gaussian normal ('g') distributions
                      type = c("c","g","g","g","g","g","g"), 
                      
                      k =2,
                      
                      # ~~ test code to see if we can get signs for tx effect ~~
                      binarySign = TRUE,
                      
                      # per Jonas set this way
                      ruleReg = "OR")
  
  return(fit_mgm)
  
}

fit_my_mgm.moderated <- function(my_data){
  
  # could examine just specific moderation effects
  # as written, allows all edges to vary by condition
  
  set.seed(08132021)
  fit_mgm <- mgm::mgm(data = my_data, 
                      
                      # first variable (condition) has 2 conditions, all others are continuous
                      level = c(2,1,1,1,1,1,1), 
                      
                      # first variable (condition) is categorical, all others 
                      # have assumed Gaussian normal ('g') distributions
                      type = c("c","g","g","g","g","g","g"), 
                      
                      moderator = 1, #check syntax
                      
                      # per Jonas set this way
                      ruleReg = "OR")
  
  return(fit_mgm)
  
}

```


# Change score models - setup and generic functions

## Create dataset of change scores

```{r}
ChangeScores_data <- data_all_timepoints %>%
  
  pivot_longer(cols = HADS.A:AAQc, names_to = 'instrument') %>%
  pivot_wider(id_cols = c('ID','instrument','timepoint', 'Condition_Dummy'),
              names_from = 'timepoint',
              values_from = 'value') %>%
  mutate(PreToMid = (`2` - `1`),
         MidToPost = (`3` - `2`),
         PostTo3mFU = (`4` - `3`),
         `3mFUTo6mFU` = (`5` - `4`),
         PreToPost = (`3` - `1`),
         PreTo6mFU = (`5` - `1`)) %>%
  # drop scores at each timepoint since change scores have now been computed
  dplyr::select(-`1`, -`2`, -`3`, -`4`, -`5`) %>%
  
  # tidy
  pivot_longer(cols = PreToMid:PreTo6mFU, names_to = 'ChangeScore') %>%
  
  # pivot to long by interval, by participant, wide by instrument
  # consistent with format we will want to estimate networks
  pivot_wider(names_from = instrument)
```

## Extract data for one interval

```{r}
getDataForInterval <- function(ChangeScores, my_interval){
  data_to_return <- ChangeScores %>% filter(ChangeScore == my_interval) %>%
    select(-ChangeScore, -ID) %>%
    
  # drop full rows with any missing observations
    drop_na()
  return(data_to_return)
}
```

## Wrappers

```{r}
runChangeScoreNetwork <- function(ChangeScore_data, my_interval, moderated = FALSE){
  
  data <- getDataForInterval(ChangeScore_data, my_interval) %>%
    as.matrix()
  
  ifelse(moderated == TRUE,
         fit <- fit_my_mgm.moderated(data),
         fit <- fit_my_mgm(data))
  
  return(fit)
}
runBootstrappedChangeScoreNetwork <- function(ChangeScore_data, my_interval, nB = 5000){
  
  data <- getDataForInterval(ChangeScore_data, my_interval) %>%
    as.matrix()
  
  fit <- fit_my_mgm(data)
  
  fit.boot <- resample(object = fit, 
                               data = data, 
                               nB = nB)
  
  return(fit.boot)
}

```

## Get data for specific intervals and save it to compute reliability

```{r}

PreToPost.data <- getDataForInterval(ChangeScores_data, 'PreToPost') %>%
    as.matrix()

PreTo6MFU.data <- getDataForInterval(ChangeScores_data, 'PreTo6mFU') %>%
    as.matrix()

write_rds(PreToPost.data, file = here('4 Generated Datasets','PreToPost.data.rds'))
write_rds(PreTo6MFU.data, file = here('4 Generated Datasets','PreTo6MFU.data.rds'))

```


# Unmoderated Change Score Network Models

## PreToPost 

```{r}

PreToPost.fit <- runChangeScoreNetwork(ChangeScores_data, 'PreToPost')

write_rds(x = PreToPost.fit, file = here('Fitted model objects',
                                         'Nonmoderated',
                                        'Nonbootstrapped',
                                        'PreToPost.fit'))



PreToPost.fit.boot <- runBootstrappedChangeScoreNetwork(ChangeScores_data, 'PreToPost')

write_rds(x = PreToPost.fit.boot, file = here('Fitted model objects','PreToPost.fit.boot'))

```
\newpage

## PreTo6mFU 
```{r}
PreTo6mFU.fit <- runChangeScoreNetwork(ChangeScores_data, 'PreTo6mFU')

write_rds(x = PreTo6mFU.fit , file = here('Fitted model objects',
                                          'Nonmoderated',
                                          'Nonbootstrapped',
                                          'PreTo6mFU.fit'))

PreTo6mFU.fit.boot <- runBootstrappedChangeScoreNetwork(ChangeScores_data, 'PreTo6mFU')

write_rds(x = PreTo6mFU.fit.boot, file = here('Fitted model objects','PreTo6mFU.fit.boot'))

PreTo6mFU.fit.boot <- read_rds(file = here('Fitted model objects','PreTo6mFU.fit.boot'))

plotRes(PreTo6mFU.fit.boot, labels = c('TX','HADS','IESR','FCR','SCS','EAC','AAQc'))
```






# Moderated Change Score Network Models


## PreToPost 

```{r}

PreToPost.moderated.fit <- runChangeScoreNetwork(ChangeScores_data, 'PreToPost', moderated = TRUE)

write_rds(x = PreToPost.moderated.fit , file = here('Fitted model objects',
                                                    'Moderated',
                                                    'Not bootstrapped',
                                                    'PreToPost.moderated.fit'))


PreToPost.moderated.fit.boot <- runBootstrappedChangeScoreNetwork(ChangeScores_data, 'PreToPost', moderated = TRUE)
  
write_rds(x = PreToPost.moderated.fit.boot , file = here('Fitted model objects',
                                                    'Moderated',
                                                    'Bootstrapped',
                                                    'PreToPost.moderated.fit.boot'))





```
\newpage

## PreTo6mFU 
```{r}
PreTo6mFU.moderated.fit <- runChangeScoreNetwork(ChangeScores_data, 'PreTo6mFU', moderated = TRUE)

write_rds(x = PreTo6mFU.moderated.fit , file = here('Fitted model objects',
                                                    'Moderated',
                                                    'Not bootstrapped',
                                                    'PreTo6mFU.moderated.fit'))

PreTo6mFU.moderated.fit.boot <- runBootstrappedChangeScoreNetwork(ChangeScores_data, 'PreTo6mFU', moderated = TRUE)
  
write_rds(x = PreTo6mFU.moderated.fit.boot , file = here('Fitted model objects',
                                                    'Moderated',
                                                    'Bootstrapped',
                                                    'PreTo6mFU.moderated.fit.boot'))


```





