---
title: "Estimate residualized change score network models"
author: Joel N Fishbein
---

This script runs network models with residualized change scores.

# Read in the data and libraries

```{r}

knitr::opts_chunk$set(error = TRUE)

library(tidyverse)
library(mgm)
library(qgraph)
library(psych)
library(corrr)
library(here)

``` 

```{r}

data_all_timepoints <- read_rds(file = here('4 Generated Datasets','Vars_At_All_Timepoints.rds'))

```


# Generic model functions


## fit MGM functions
```{r}

fit_my_mgm <- function(my_data){
  
  set.seed(08132021)
  fit_mgm <- mgm::mgm(data = my_data, 
                      
                      # first variable (condition) has 2 conditions, all others are continuous
                      level = c(2,1,1,1,1,1,1), 
                      
                      # first variable (condition) is categorical, all others 
                      # have assumed Gaussian normal ('g') distributions
                      type = c("c","g","g","g","g","g","g"), 
                      
                      k =2,
                      
                      # ~~ test code to see if we can get signs for tx effect ~~
                      binarySign = TRUE,
                      
                      # per Jonas set this way
                      ruleReg = "OR")
  
  return(fit_mgm)
  
}

fit_my_mgm.moderated <- function(my_data){
  
  # could examine just specific moderation effects
  # as written, allows all edges to vary by condition
  
  set.seed(08132021)
  fit_mgm <- mgm::mgm(data = my_data, 
                      
                      # first variable (condition) has 2 conditions, all others are continuous
                      level = c(2,1,1,1,1,1,1), 
                      
                      # first variable (condition) is categorical, all others 
                      # have assumed Gaussian normal ('g') distributions
                      type = c("c","g","g","g","g","g","g"), 
                      
                      moderator = 1, #check syntax
                      
                      # per Jonas set this way
                      ruleReg = "OR")
  
  return(fit_mgm)
  
}

fit_my_boot_mgm <- function(fit, nB = 5000, myData){
  
  fit.boot <- resample(object = fit, 
                               data = myData, 
                               nB = nB)
  
  return(fit.boot)
}

```

# Compute residualized change scores

## Pre Post

```{r}

data.PrePost.wide <- 
  data_all_timepoints %>%
  
  # not analyzing CESD so drop this variable
  select(-CESD) %>% 
  
  # just Pre Post data
  filter(timepoint %in% c(1,3)) %>%
  
  # reshape data
  pivot_longer(cols = HADS.A:AAQc) %>%
  pivot_wider(names_from = c('name','timepoint')) %>%
  mutate(.rownames = as.character(c(1:nrow(.)))) %>%
  relocate(.rownames) %>%
  drop_na()  # drop incomplete cases since network analysis requires complete cases


```

### HADS.A

```{r}

HADS.A.PrePost.model <- lm(HADS.A_3 ~ HADS.A_1, data = data.PrePost.wide)

HADS.A.PrePost.resid<- broom::augment(HADS.A.PrePost.model) %>%
  pluck('.resid')

```

### IESR.Total

```{r}

IESR.Total.PrePost.model <- lm(IESR.Total_3 ~ IESR.Total_1, data = data.PrePost.wide)

IESR.Total.PrePost.resid <- broom::augment(IESR.Total.PrePost.model) %>%
  pluck('.resid')

```

### FCR

```{r}

FCR.PrePost.model <- lm(FCR_3 ~ FCR_1, data = data.PrePost.wide)

FCR.PrePost.resid <- broom::augment(FCR.PrePost.model) %>%
  pluck('.resid')

```


### SCS

```{r}

SCS.PrePost.model <- lm(SCS_3 ~ SCS_1, data = data.PrePost.wide)

SCS.PrePost.resid<- broom::augment(SCS.PrePost.model) %>%
  pluck('.resid')

```

### EAC Total

```{r}

EAC.Total.PrePost.model <- lm(EAC.Total_3 ~ EAC.Total_1, data = data.PrePost.wide)

EAC.Total.PrePost.resid<- broom::augment(EAC.Total.PrePost.model) %>%
  pluck('.resid')

```

### AAQc 

```{r}

AAQc.PrePost.model <- lm(AAQc_3 ~ AAQc_1, data = data.PrePost.wide)

AAQc.PrePost.resid<- broom::augment(AAQc.PrePost.model) %>%
  pluck('.resid')

```


### Create combined dataset

```{r}

residualized.PrePost.tibble<- 
  tibble(data.PrePost.wide %>% select(Condition_Dummy),
         HADS.A.PrePost.resid,
         IESR.Total.PrePost.resid,
         FCR.PrePost.resid,
         SCS.PrePost.resid,
         EAC.Total.PrePost.resid,
         AAQc.PrePost.resid) 

residualized.PrePost.matrix <- 
  residualized.PrePost.tibble %>%
  as.matrix()



```

## Save tibble for use in the standard mediation models

```{r}

write_rds(x = residualized.PrePost.tibble, file = here('4 Generated Datasets',
                                          'residualized.PrePost.tibble'))

```


## Pre FU

```{r}

data.PreFU.wide <- 
  data_all_timepoints %>%
  
  # not analyzing CESD so drop this variable
  select(-CESD) %>% 
  
  # just Pre Post data
  filter(timepoint %in% c(1,5)) %>%
  
  # reshape data
  pivot_longer(cols = HADS.A:AAQc) %>%
  pivot_wider(names_from = c('name','timepoint')) %>%
  mutate(.rownames = as.character(c(1:nrow(.)))) %>%
  relocate(.rownames) %>%
  drop_na()  # drop incomplete cases since network analysis requires complete cases


```

### HADS.A

```{r}

HADS.A.PreFU.model <- lm(HADS.A_5 ~ HADS.A_1, data = data.PreFU.wide)

HADS.A.PreFU.resid<- broom::augment(HADS.A.PreFU.model) %>%
  pluck('.resid')

```

### IESR.Total

```{r}

IESR.Total.PreFU.model <- lm(IESR.Total_5 ~ IESR.Total_1, data = data.PreFU.wide)

IESR.Total.PreFU.resid <- broom::augment(IESR.Total.PreFU.model) %>%
  pluck('.resid')

```

### FCR

```{r}

FCR.PreFU.model <- lm(FCR_5 ~ FCR_1, data = data.PreFU.wide)

FCR.PreFU.resid <- broom::augment(FCR.PreFU.model) %>%
  pluck('.resid')

```


### SCS

```{r}

SCS.PreFU.model <- lm(SCS_5 ~ SCS_1, data = data.PreFU.wide)

SCS.PreFU.resid<- broom::augment(SCS.PreFU.model) %>%
  pluck('.resid')

```

### EAC Total

```{r}

EAC.Total.PreFU.model <- lm(EAC.Total_5 ~ EAC.Total_1, data = data.PreFU.wide)

EAC.Total.PreFU.resid<- broom::augment(EAC.Total.PreFU.model) %>%
  pluck('.resid')

```

### AAQc 

```{r}

AAQc.PreFU.model <- lm(AAQc_5 ~ AAQc_1, data = data.PreFU.wide)

AAQc.PreFU.resid<- broom::augment(AAQc.PreFU.model) %>%
  pluck('.resid')

```


### Create combined dataset

```{r}

residualized.PreFU.tibble<- 
  tibble(data.PreFU.wide %>% select(Condition_Dummy),
         HADS.A.PreFU.resid,
         IESR.Total.PreFU.resid,
         FCR.PreFU.resid,
         SCS.PreFU.resid,
         EAC.Total.PreFU.resid,
         AAQc.PreFU.resid) 

residualized.PreFU.matrix<-
  residualized.PreFU.tibble %>%
  as.matrix()

```

## Save tibble for use in the standard mediation models

```{r}

write_rds(x = residualized.PreFU.tibble, file = here('4 Generated Datasets',
                                          'residualized.PreFU.tibble'))

```

# Fit unmoderated network models

## Pre-Post

```{r}

PrePost.residualized.fit<- fit_my_mgm(residualized.PrePost.matrix)

write_rds(x = PrePost.residualized.fit , file = here('Fitted model objects',
                                          'Residual Networks',
                                          'Nonmoderated',
                                          'Nonbootstrapped',
                                          'PrePost.residualized.fit'))

```

## Pre-FU

```{r}

PreFU.residualized.fit<- fit_my_mgm(residualized.PreFU.matrix)

write_rds(x = PreFU.residualized.fit , file = here('Fitted model objects',
                                          'Residual Networks',
                                          'Nonmoderated',
                                          'Nonbootstrapped',
                                          'PreFU.residualized.fit'))

```



# Fit moderated network models

## Pre-Post

```{r}

PrePost.moderated.residualized.fit<- fit_my_mgm.moderated(residualized.PrePost.matrix)

write_rds(x = PrePost.residualized.fit , file = here('Fitted model objects',
                                          'Residual Networks',
                                          'Moderated',
                                          'Nonbootstrapped',
                                          'PrePost.moderated.residualized.fit'))

```

## Pre-FU

```{r}

PreFU.moderated.residualized.fit<- fit_my_mgm.moderated(residualized.PreFU.matrix)

write_rds(x = PreFU.residualized.fit , file = here('Fitted model objects',
                                          'Residual Networks',
                                          'Moderated',
                                          'Nonbootstrapped',
                                          'PreFU.moderated.residualized.fit'))

```

# Bootstrap

```{r}
set.seed(08132021)

```

## Pre-Post


```{r}

PrePost.fit.boot <- fit_my_boot_mgm(PrePost.residualized.fit, 
                                    nB = 5000, 
                                    myData = residualized.PrePost.matrix)

write_rds(x = PrePost.fit.boot , file = here('Fitted model objects',
                                          'Residual Networks',
                                          'Nonmoderated',
                                          'Bootstrapped',
                                          'PrePost.residualized.boot.fit'))

```

```{r}

PreFU.fit.boot <- fit_my_boot_mgm(PreFU.residualized.fit, 
                                  nB = 5000, 
                                  myData = residualized.PreFU.matrix)

write_rds(x = PreFU.fit.boot , file = here('Fitted model objects',
                                          'Residual Networks',
                                          'Nonmoderated',
                                          'Bootstrapped',
                                          'PreFU.residualized.boot.fit'))

```


# Bootstrap

```{r}
set.seed(08132021)

```

## Pre-Post

### Non moderated

```{r}

PrePost.fit.boot <- fit_my_boot_mgm(PrePost.residualized.fit, 
                                    nB = 5000, 
                                    myData = residualized.PrePost.matrix)

write_rds(x = PrePost.fit.boot , file = here('Fitted model objects',
                                          'Residual Networks',
                                          'Nonmoderated',
                                          'Bootstrapped',
                                          'PrePost.residualized.boot.fit'))



```

```{r}

PreFU.fit.boot <- fit_my_boot_mgm(PreFU.residualized.fit, 
                                  nB = 5000, 
                                  myData = residualized.PreFU.matrix)

write_rds(x = PreFU.fit.boot , file = here('Fitted model objects',
                                          'Residual Networks',
                                          'Nonmoderated',
                                          'Bootstrapped',
                                          'PreFU.residualized.boot.fit'))

```




### Moderated

```{r}

# PrePost.moderated.fit.boot <- fit_my_boot_mgm(PrePost.moderated.residualized.fit,
#                                     nB = 3,
#                                     myData = residualized.PrePost.matrix)
# 
# write_rds(x = PrePost.moderated.fit.boot , file = here('Fitted model objects',
#                                           'Residual Networks',
#                                           'Moderated',
#                                           'Bootstrapped',
#                                           'PrePost.moderated.residualized.boot.fit'))

```


