---
title: "Network of variables at Pre"
output: html_notebook
---
Per Jonas's suggestion I will attempt to model no more than 8 variables simultaneously.

The seven variables Joanna and I chose in descending order of importance to keep in the model are:

HADS-A (drop first among anx measures?)
IES-R
FCR
Self Compassion
EAC
AAQc
CESD

# Read in the data and libraries

```{r}
library(tidyverse)
library(bootnet)
library(psych)
library(skimr)  
library(corrr)

``` 

```{r}
data <- read_rds(file = here('4 Generated Datasets','Vars_At_Pre_Data.rds'))
presence <- read_rds(file = here('4 Generated Datasets','Vars_At_Pre_Presence.rds'))

```

# Examine univariates

Distributions look ok.

```{r}
data %>%  
  select(-ID, -Condition_Dummy, -Condition) %>%
  psych::describe()
  

```

# Examine bivariates

No correlations looking too high here which is good...

corrr package used for easy computation and display of the correlation matrix

```{r}

data %>%
  select(-ID, -Condition_Dummy, -Condition) %>%
  corrr::correlate() %>%
  corrr::rearrange() %>%
  corrr::shave() %>%
  corrr::fashion()
  
```

# Estimate network model


