---
author: Joel N. Fishbein, M.A.
date: December 11, 2022
---

# Read in data

```{r}
library(tidyverse)
library(here)
library(qgraph)

PreToPost.Diffscore.fit <- read_rds(here('Fitted model objects','Nonmoderated','Nonbootstrapped','PreToPost.fit'))
PreTo6mFU.Diffscore.fit <- read_rds(here('Fitted model objects','Nonmoderated','Nonbootstrapped','PreTo6mFU.fit'))

PreToPost.Residualized.fit <- read_rds(
  here('Fitted model objects/Residual Networks/Nonmoderated/Nonbootstrapped',
       'PrePost.residualized.fit'))

PreToFU.Residualized.fit <- read_rds(
  here('Fitted model objects/Residual Networks/Nonmoderated/Nonbootstrapped',
       'PreFU.residualized.fit'))


```


# Hardcoded layout

This is the saved layout from the difference score Pre Post network model based on the parameters passed in. This layout looks quite good for the variables of interest to us and it's helpful to display all the networks on the same layout. So for simplicity I've just hardcoded in the values here.

```{r}

best_layout <-matrix(
  c( -0.01058774, -1.00000000, -0.75129002,  0.80844598,  1.00000000, -0.15968250,  0.16730796, 0.06435805,  0.26700354, -0.70058357,  0.52548735, -0.46997918,  1.00000000, -1.00000000),
  nrow = 7, ncol = 2)

```

## generic function to plot MGM
```{r}

plot_my_mgm <- function(my_mgm_fit){
  
  my_edgeweights <- my_mgm_fit$pairwise$wadj
  
  my_colorblind_edge_colors <- my_mgm_fit$pairwise$edgecolor_cb
  
  set.seed(1)
  
  my.groups <- c(rep("Condition Assignment",1),rep("Outcome",3),rep("Process",3))
                #list(1, 2:4, 5:7)
  
  return(qgraph(my_edgeweights, 
                #layout = 'circle',
                layout = 'spring', # Fruchterman-Reingold alg
                repulsion = .47,
                edge.label.cex = 0.75, # edge text size
                edge.color = my_colorblind_edge_colors, 
                legend.cex=.3, 
                edge.labels = FALSE,
                groups = my.groups,
             theme = 'colorblind',
                legend = FALSE,
                vsize = 3.5, esize = 15, labels = #c('COND','HADS','IESR','CARS','SCS','EAC','AAQc'))
                  c('ACT/\nMEUC','Anxiety','Trauma','Recur \nFear','Self-\nComp','EAC','Avoid')))
}
  
```

# Difference Score Plots

## generate plot but don't save yet

```{r}

PreToPost.Diffscore.plot <- plot_my_mgm(PreToPost.Diffscore.fit)
PreTo6mFU.Diffscore.plot <- plot_my_mgm(PreTo6mFU.Diffscore.fit)


```


## Output plots for each interval

```{r}


qgraph::qgraph(PreToPost.Diffscore.plot, title.cex = 2, title = "", 
               node.width = 3,  edge.label.cex = 1, # edge text size
               filetype = 'png', filename = here('Plots','Pre to Post Difference Score Sample Network'))


qgraph::qgraph(PreTo6mFU.Diffscore.plot, title.cex = 2, title = "", 
               node.width = 3,  edge.label.cex = 1, # edge text size
               layout = best_layout, # reuse plot from Pre-Post
               filetype = 'png', filename = here('Plots','Pre to FU Difference Score Sample Network'))


```





# Residualized Change Score Plots

## generate plot but don't save yet

```{r}

PreToPost.Residualized.plot <- plot_my_mgm(PreToPost.Residualized.fit)
PreTo6mFU.Residualized.plot <- plot_my_mgm(PreToFU.Residualized.fit)


```


## Output plots for each interval

```{r}


qgraph::qgraph(PreToPost.Residualized.plot, title.cex = 2, title = "", 
               node.width = 3,  edge.label.cex = 1, # edge text size
               layout = best_layout, 
               filetype = 'png', filename = here('Plots','Pre to Post Residualized Score Sample Network'))


qgraph::qgraph(PreTo6mFU.Residualized.plot, title.cex = 2, title = "", 
               node.width = 3,  edge.label.cex = 1, # edge text size
               layout = best_layout, 
               filetype = 'png', filename = here('Plots','Pre to FU Residualized Score Sample Network'))


```


