---
author: Joel N. Fishbein, M.A.
date: December 11, 2022
---

# read data and libraries

```{r}

library(tidyverse)
library(here)
library(lavaan)


# PreToPost.data <- readRDS(file = here('4 Generated Datasets','Vars_At_All_Timepoints.rds')) %>%
#   as_tibble() %>%
#   select(-CESD) %>%
#   pivot_longer(cols = HADS.A:AAQc) %>%
#   filter(timepoint %in% c(1,3)) %>%
#   pivot_wider(names_from = timepoint:name, names_glue = "{name}_T{timepoint}") %>%
#   filter(complete.cases(.))
```

# Run models with simple lavaan code (using precalculated residual scores)

## Read in residualized scores (computed in the script that runs the residualized change score network models)

```{r}

PrePost.residualized.tibble <- read_rds(file = here('4 Generated Datasets',
                                          'residualized.PrePost.tibble'))

PreFU.residualized.tibble <- read_rds(file = here('4 Generated Datasets',
                                          'residualized.PreFU.tibble'))

```

## Generic mediation model

### Pre-Post

```{r}

runPrePostMediationModel <- function(mediator_var, outcome_var) {
  mediation.model.generic <- '

Mediator.PrePost.resid ~ a*Condition_Dummy
Outcome.PrePost.resid ~ b*Mediator.PrePost.resid
Outcome.PrePost.resid ~ cprime*Condition_Dummy

# !Estimate of mediated effect;
ab := a*b

'
  # this line inserts the actual variable names into the model syntax
  # as specified above
  mediation.model <-  str_replace_all(mediation.model.generic,
                                      c("Outcome" = outcome_var,
                                        "Mediator" = mediator_var))
  # model is estimated
  mediation.fit <- lavaan::sem(model = mediation.model,
                               data = PrePost.residualized.tibble,
                               bootstrap = 10000,
                               se = 'bootstrap',
                               missing = 'fiml')
  return(mediation.fit)
}

```

### Pre-FU

```{r}

runPreFUMediationModel <- function(mediator_var, outcome_var) {
  mediation.model.generic <- '

Mediator.PreFU.resid ~ a*Condition_Dummy
Outcome.PreFU.resid ~ b*Mediator.PreFU.resid
Outcome.PreFU.resid ~ cprime*Condition_Dummy


# !Estimate of mediated effect;
ab := a*b

'
  # this line inserts the actual variable names into the model syntax
  # as specified above
  mediation.model <-  str_replace_all(mediation.model.generic,
                                      c("Outcome" = outcome_var,
                                        "Mediator" = mediator_var))
  # model is estimated
  mediation.fit <- lavaan::sem(model = mediation.model,
                               data = PreFU.residualized.tibble,
                               bootstrap = 10000,
                               se = 'bootstrap',
                               missing = 'fiml')
  return(mediation.fit)
}

```

## Run models

## EAC Models

```{r}
set.seed(1)
EAC.Mean_IESR.Total_contemporaneous.fit <- runPrePostMediationModel('EAC.Total','IESR.Total')

set.seed(1)
EAC.Mean_FCR_contemporaneous.fit <- runPrePostMediationModel('EAC.Total','FCR')


set.seed(1)
EAC.Mean_HADS.A_contemporaneous.fit <- runPrePostMediationModel('EAC.Total','HADS.A')

```

## SCS Models

```{r}
set.seed(1)
SCS_IESR.Total_contemporaneous.fit <- runPrePostMediationModel('SCS','IESR.Total')
set.seed(1)
SCS_FCR_contemporaneous.fit <- runPrePostMediationModel('SCS','FCR')
set.seed(1)
SCS_HADS.A_contemporaneous.fit <- runPrePostMediationModel('SCS','HADS.A')
```

## AAQc Models

```{r}
set.seed(1)
AAQc_IESR.Total_contemporaneous.fit <- runPrePostMediationModel('AAQc','IESR.Total')
set.seed(1)
AAQc_FCR_contemporaneous.fit <- runPrePostMediationModel('AAQc','FCR')
set.seed(1)
AAQc_HADS.A_contemporaneous.fit <- runPrePostMediationModel('AAQc','HADS.A')
```

# save model output to a file

Since these models take a long time to run, save the actual output.

```{r}
# remove objects from the environment
# so that individual scores are not saved alongside the models
rm(PrePost.residualized.tibble)
rm(PreFU.residualized.tibble)
rm(runPreFUMediationModel)
rm(runPrePostMediationModel)
# save the rest of the workspace, which is now just lavaan fit models
# and the generic functions
save.image(file = here('4 Generated Datasets', 'PrePost_mediation_models_residualized.RData'))
```
